%-------------------------
% Resume in Latex
% Author : igor kan
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{kotex}
\usepackage[normalem]{ulem}   % in preamble

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
            {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
    \begin{center}
        \textbf{\Huge \scshape Igor Kang} \\ \vspace{1pt}
        \small 010-3375-5331 $|$
        \href{mailto:x@x.com}{\uline{ikanv13@gmail.com}} $|$
        \href{https://linkedin.com/in/rocket13}{\uline{linkedin.com/in/rocket13}} $|$
        \href{https://github.com/igorkang-smc}{\uline{github.com/igorkang-smc}} $|$
        \href{https://igorkang.notion.site/Portfolio-25bc1bafd5148063a160eb2fd609a4f1}{\uline{portfolio}}
    \end{center}

%-----------EDUCATION-----------
    \section{Education}
    \resumeSubHeadingListStart
    \resumeSubheading
    {Lomonosov Moscow State University}{Tashkent, Uzbekistan}
    {B.S. in Applied Mathematics and Computer Science}{Sep. 2015 – Jun. 2019}
    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
    \section{Experience}
    \resumeSubHeadingListStart

    \resumeSubheading
    {Backend Developer}{Apr. 2022 – Mar. 2025}
    {The SMC Group}{Seoul, Korea}
    \resumeItemListStart
    \resumeItem{Designed and deployed AI agents, chatbots, and internal AI apps, accelerating R\&D speed}
    \resumeItem{Built scalable APIs and backends with AWS Lambda, FastAPI, Laravel, and Django, supporting 1000+ users}
    \resumeItem{Automated infrastructure and CI/CD with K8S, AWS, Docker, and Terraform, reducing deployment time}
    \resumeItemListEnd

    \resumeSubheading
    {Team Lead Developer}{Sep. 2021 – Feb. 2022}
    {Taein Education Co., Ltd.}{Seongnam, Korea}
    \resumeItemListStart
    \resumeItem{Built core products with Java Spring Framework, contributing to improved platform stability}
    \resumeItem{Developed responsive frontends (SPA, landing pages, back-office) using CSS, JS (jQuery), React, and Vue.js}
    \resumeItem{Coordinated project delivery through effective collaboration with departments and clients}
    \resumeItemListEnd

    \resumeSubheading
    {Junior Developer}{Jan. 2020 – Jan. 2021}
    {Click Co., Ltd.}{Tashkent, Uzbekistan}
    \resumeItemListStart
    \resumeItem{Maintained critical payment systems and handlers, ensuring stable transaction processing}
    \resumeItem{Provided technical support and system integration, including payment gateway testing}
    \resumeItem{Developed and managed back-office solutions to streamline business operations}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
    \section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
    {\textbf{Smart Space AI} $|$ \emph{Python, FastAPI, LangChain, OpenAI API, PostgreSQL, Docker}}{Jan. 2025 – Mar. 2025}
    \resumeItemListStart
    \resumeItem{Developed a FastAPI backend providing a REST API integrated with OpenAI and LangChain SQLAgent}
    \resumeItem{Built and managed a unified database of bookable spaces across two company offices}
    \resumeItem{Deployed the service and implemented CI/CD pipelines for monitoring and rapid redeployment}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Dunkin Homepage} $|$ \emph{Laravel, MySQL, AWS, Inertia.js, Git}}{Aug. 2023 – Sep. 2024}
    \resumeItemListStart
    \resumeItem{Developed backend with Laravel and Inertia.js, collaborating with external designers and frontend developers}
    \resumeItem{Deployed and configured the application on AWS infrastructure, including server and database setup}
    \resumeItem{Maintained stability and client satisfaction through continuous UI improvements and feature updates}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Baskin Robbins Homepage} $|$ \emph{AWS, PHP, JS, Git}}{Jun. 2023 – Jun. 2024}
    \resumeItemListStart
    \resumeItem{Maintained and extended a high-traffic website for a leading ice cream brand}
    \resumeItem{Implemented major features such as Happy Point authentication and a customer feedback/complaint system}
    \resumeItem{Managed deployment on AWS, ensuring stable and reliable service operation}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
    \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
            \textbf{Languages}{: Python, PHP, Java, SQL, NoSQL, JavaScript, HTML/CSS} \\
            \textbf{Frameworks}{: FastAPI, Django, Laravel, React, Spring Boot} \\
            \textbf{Developer Tools}{: Git, Docker, Kubernetes, Terraform, Redis, AWS, GraphQL, Jenkins, Prometheus, Grafana} \\
            \textbf{Libraries}{: Django REST Framework, SQLModel, Pydantic, Uvicorn, Pytest, LangChain}
        }}
    \end{itemize}

%-------------------------------------------
\end{document}
